### 2014-01-21 intro.tex
Kathy's changes

The goal of this study is to evaluate the ability of ARFI imaging to delineate
prostate zonal anatomy, specifically central gland and total prostate gland
\invivo as compared to endorectal MR T2WI.  Section~\ref{sect:background}
provides an overview of MR and ARFI imaging in the prostate and an overall
clinical motivation for prostate imaging.  Section~\ref{sect:methods} describes
the methods used to experimentally-acquire our imaging data, process of gross
pathological specimens post radical prostatectomy, and image process our
datasets.  The results of our analysis, including gross pathology and imaging
prostate axis and volume estimates, are presented in
Section~\ref{sect:results}, along with a statistical analysis of the bias and
variability associated with each imaging modalities measurements, all of which
is discussed in Section~\ref{sect:discussion}.

>>>>

The goal of this study is to evaluate the ability of ARFI imaging to delineate
prostate zonal anatomy, specifically central gland and total prostate gland
\invivo as compared to endorectal MR T2WI.  Section~\ref{sect:background}
provides an overview of MR and ARFI imaging in the prostate and an overall
clinical motivation for prostate imaging.  Section~\ref{sect:methods} describes
the methods used to experimentally-acquire our imaging data, process the gross
pathological specimens post radical prostatectomy, and image process our
datasets.  The results of our analysis, including gross pathology and imaging
prostate axis and volume estimates, are presented in
Section~\ref{sect:results}, along with a statistical analysis of the bias and
variability associated with each imaging modalities measurements, all of which
is discussed in Section~\ref{sect:discussion}.
